Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-07 publication_materials/ms_rbc.tex
abstract rev2b

\begin{abstract}
A novel quasilinear form of the Boussinesq Rayleigh-B\'enard equations is derived from the classical linear stability analysis. Eigenfunction amplitudes are obtained by requiring marginal-stability. Symmetric thermally-equilibrated states are then obtained and their properties are analyzed. Such states are compared with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers which scale like $\delta \sim Ra^{-1/3}$. 2-dimensional simulations are initialized with solutions to the quasilinear problem;
they do not undergo a convective transient period but turn out to be kinetically exaggerated.
\end{abstract}

@@

\section{Introduction}
Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings. Our understanding of highly turbulent convective systems is generally limited by the prohibitive computational costs associated with direct numerical simulations \cite{Zhu}. There exists a substantial body of work concerning the asymptotic scaling laws of such systems with no general consensus. Reduced models are particularly useful in this context because they allow us to study the underlying behavior of turbulent convection with relatively low expense. 
\par In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh–Bénard convection equations using a strategy similar to \cite{Chini_sw}. This is realized by solving the linearized equations and evolving a mean temperature profile according to the perturbation variables. In general, each set of perturbations has an arbitrary amplitude which we obtain by imposing marginal stability. The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features. 

>>>>

\begin{abstract}
Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number limit.
In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
We compare these solutions with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$. 
We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
\end{abstract}

@@

\section{Introduction}
Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings. Our understanding of turbulent convective systems is generally limited by the prohibitive computational costs associated with direct numerical simulations \cite{Zhu}. There exists a substantial body of work concerning the asymptotic scaling laws of such systems with no general consensus. Reduced models are particularly useful in this context because they allow us to study the underlying behavior of turbulent convection with relatively low expense.

In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh–Bénard convection equations using a strategy similar to \cite{Chini_sw}. This is realized by solving the linearized equations and evolving a mean temperature profile according to the perturbation variables. In general, each set of perturbations has an arbitrary amplitude which we obtain by imposing marginal stability. The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features. 
